---
title: "Work 20210707"
author: "Guangyou Li"
date: 2021-07-07
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```


This is a review of my work for previous two weeks.

# Study

  * [PoPs:Leveraging polygenic enrichments of gene features to predict genes underlying complex traits and diseases](https://doi.org/10.1101/2020.09.08.20190561)

  * [A practical introduction to statistical genetics](https://rawgit.com/uqrmaie1/statgen_equations/master/statgen_equations.html)

  * [Dockerfile writing](https://github.com/cumc/bioworkflows/blob/master/GWAS/lmm.dockerfile)

  * [Statistical genetics papers](http://statgen.us/lab-wiki/learning_center/statgen-papers#introductory)

# Work review

  * [GWAS_QC memory problem](https://github.com/UxxUnet/prototype/blob/main/GWAS_QC_Rmem.ipynb)

  * [PCA plot problem](https://github.com/UxxUnet/prototype/blob/main/PCA_plot_problem.ipynb)

  * [bcfstats TsTv extraction](https://github.com/UxxUnet/prototype/blob/main/bcfstatsextract.ipynb)

  * [PoPs](https://github.com/UxxUnet/prototype/blob/main/bcfstatsextract.ipynb)

# Future work

  * [Variant calling pipeline modification](https://github.com/cumc/bioworkflows/blob/master/variant-calling/gatk_joint_calling.ipynb)   
  * [ANNOVAR](https://annovar.openbioinformatics.org/en/latest/)